\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2021-05-04 public/paper/sub-2-arxiv/pyg4ometry.tex

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%%\documentclass[final,5p,times]{elsarticle}
%\documentclass[final,5p,times,twocolumn]{elsarticle}
\documentclass[preprint,12pt]{elsarticle}

@@

\section{Author contributions}
{\bf Stewart Boogert}: conceptualization, supervision, methodology, software, validation and writing - original draft. 
{\bf Stuart Walker}: methodology, software, validation and writing - original draft (FLUKA components). 
{\bf Andrey Abramov}: software, validation and writing - review \& editing (Geant4 and GDML). 
{\bf Laurence Nevay}: software, validation and writing - review \& editing. 
{\bf William Shields}: software (GDML), validation and writing - review \& editing

>>>>

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%\documentclass[final,5p,times,twocolumn]{elsarticle}
\documentclass[preprint,12pt]{elsarticle}

@@
